Responses to the Reviewers' Comments

### 2024-10-21 Response/Paper_Res.tex
Rev_V6.6

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{enumerate}[]
\item We have devoted Section II of the revised manuscript to the literature review and provided a survey of the recently published state-of-the-art works.
\item Furthemore, we have expanded the explanations about each related work and discussed their pros/cons.
\end{enumerate}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. We have also included a table to provide a comprehensive comparison of the related works. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table111} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

@@

\underline{Authors' Reply}: (a) Task sizes are chosen from a discrete set as most applications have tasks with predefined sizes. For instance, in image and video processing, tasks are typically divided into standardized sizes [X,XX,XXX]. Therefore, we assume that task sizes are selected randomly and uniformly from this discrete set. To address the reviewer’s comment and to provide further clarity regarding task sizes, we have revised the second paragraph of Section II as follows.

@@

\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_1} 
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\caption{\textcolor{blue}{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart1}
\end{figure}\vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart2}
\end{figure}\vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart3}
\end{figure} 
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_2} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_1}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

@@

Furthermore, to enhance the evaluation of our work, we have extended the performance analysis by comparing QECO with vanilla DQN and DDQN \cite{van2016deep}. This comparison illustrates the impact of Dueling DQN, Double DQN, and LSTM network techniques. We have added Fig. 7 to Section V of the revised manuscript.

@@

\,\,\,\,We further investigate the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE. This metric signifies the advantages MDs obtain by utilizing different algorithms. Fig.~\ref{chart44} (a) shows the average QoE for different values of the task arrival rate. This figure highlights the superiority of the QECO algorithm in providing MDs with an enhanced experience. At lower task arrival rates (i.e., 50-150), QECO performs optimally and maintains an average QoE of at least 0.72, while the other methods experience a steeper decline, with average QoE dropping to 0--0.54. Specifically, at a task arrival rate of 200, QECO improves the average QoE by 91.7\% compared to DCDRL in the positive average QoE range. As task arrival rates increase to 300, the average QoE significantly decreases for all methods due to increased competition for resources in the MEC system. However, QECO still maintains a positive average QoE, while other methods fall to negative values, with a decline of up to -0.17. For higher task arrival rates (i.e., 350–450), QECO experiences a negative average QoE, but it shows at least a 42.6\% and 24.6\% smaller reduction in average QoE compared to RD and DCDRL, respectively. \vspace{3mm}

\,\,\,\,Fig.~\ref{chart44} (b) illustrates the average QoE when we increase the number of MDs. The EN's workload grows when there are a larger number of MDs, leading to a reduction in the average QoE of all methods except LC. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases from 30 to 110, QECO consistently maintains at least a 29.8\% higher QoE compared to the other methods. Specifically, at a moderate number of 70 MDs, QECO achieves an average QoE of 0.57, showing a 60.3\% improvement compared to DCDRL. It is worth noting that although improvements in each of the QoE factors can contribute to enhancing system performance, it is essential to consider the user's demands in each time slot. Therefore, the key difference between QECO and other methods is that it prioritizes users' demands, enabling it to strike an appropriate balance among them, ultimately leading to a higher QoE for MDs. \vspace{3mm}\\\dots }}

@@

\,\,\,\, To capture the interactions between agents and the environment, we carefully simulated an MEC system that allows the DRL agents to gain experience and generate the data required in the proper format for training. As the agent interacts with the environment, it generates new data at each time step, using the system’s feedback (e.g., QoE) to adjust its actions. As mentioned in Section III of the revised manuscript, based on Queuing Theory, our simulated model provides key system performance metrics (for example, task delay, energy consumption, and others), which enable the agent to determine the mobile device's QoE and evaluate each state-action advantage value.\vspace{2mm}

\,\,\,\, For data generation, we adopt a scenario comprising 1,000 episodes. Each episode contains 100 time slots, each of length 0.1 seconds. During each time slot, mobile devices generate computation tasks based on a probabilistic task generation model. The DRL agents make offloading decisions for newly arrived tasks based on their state, which includes information such as task size, queue lengths, the mobile device’s energy level, and the workload history at the edge nodes. The agent evaluates the impact of its actions on the state by assessing the mobile device's QoE, which reflects key performance metrics based on user preferences. The system then transitions to the next state, enabling mobile devices to accumulate the necessary experience through interactions with the MEC environment. As detailed in Section IV-B, these experiences are stored in the replay buffer, creating a rich, continuously growing dataset that represents the diverse conditions and scenarios the agent encounters during computation offloading in MEC.\vspace{2mm}

@@

(c) Indeed, QECO improves the number of completed tasks by 12.2\% while at the same time reduces task delay and energy consumption by 11.7\% and 10.8\%, respectively. These together contribute to a significant improvement  in average QoE compared to \cite{qiu2020distributed}. To clarify the improvement obtained by QECO, we have revised the abstract, Section I, and Section VI as follows.

@@

				Simulation results with 50 mobile devices and 5 edge nodes validate that the QECO algorithm is able to efficiently recognize the mobile devices' demands and exploit the computational resources of edge nodes. 
				Consequently, it increases the number of completed tasks by 12.2\%, while simultaneously reducing task delay and energy consumption by 11.7\% and 10.8\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of at least 34.8\% compared to an existing algorithm.
}

@@

	\underline{Authors' Reply}: To address the reviewer's comment, we have carefully studied the recently published papers and revised the manuscript. 
	To be more specific,

		We have extended the literature review in Section II of the revised manuscript by providing a more comprehensive survey of the recently published state-of-the-art works and comparing their characteristics in Table \ref{table11}.
		We have compared our work with more existing works and extended the performance evaluation in Section VI of the revised manuscript.

\vspace{6mm}
 The newly added Section II of the revised manuscript is as follows.

@@

		To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.
		Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the IIoT systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
		To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.

@@

		\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
			While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
			QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}

		\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}
		Our main contributions are summarized as follows:
		\begin{itemize}
			\item \textit{Task Offloading Problem in the MEC System:} We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of mobile devices (MDs), this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs. \vspace{2mm}

			\item \textit{DRL-based Offloading Algorithm:} To address the problem of long-term QoE maximization, we focus on task completion, task delay, and energy consumption to quantify the MDs' QoE. We propose QECO algorithm based on DRL that empowers each MD to make offloading decisions independently, without prior knowledge of the other MDs' tasks and offloading models. With a focus on the MD's energy level, our approach leverages dueling double deep Q-network (D3QN) \cite{wang2016dueling} to prioritize and strike an appropriate balance between QoE factors. To handle the uncertainty of workloads at ENs, we integrate long short-term memory (LSTM) \cite{hochreiter1997long} into D3QN, enabling MDs to forecast ENs' workloads over time and improve the estimation of long-term QoE. Additionally, we provide an analysis of the training convergence and computational complexity of the proposed algorithm. \vspace{2mm}

			\item \textit{Performance Evaluation:} We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to DQN and D3QN methods, while providing a substantial improvement of at least 34.8\% in average QoE. This advantage is achieved through prioritizing MD's QoE preferences, resulting in improvements of at least 12.2\%, 11.7\%, and 10.8\% in the average number of completed tasks, task delay, and energy consumption, respectively, when compared to the distributed and collective DRL-based offloading algorithm (DCDRL) \cite{qiu2020distributed} and several benchmark methods.

@@

	}

\end{my} \vspace{6mm}

We extended the evaluation of the QECO algorithm by comparing it with DCDRL \cite{qiu2020distributed}, which is a distributed algorithm for delay-sensitive tasks based on the actor-critic framework. This is the foundation for many state-of-the-art DRL algorithms, including DDPG and PPO. We have added this comparison to Section VI of the revised manuscript as follows: \newline

>>>>

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{enumerate}[]
\item We have devoted Section II of the revised manuscript to the literature review and provided a survey of the recently published state-of-the-art works.
\item Furthemore, we have expanded the explanations about each related work and discussed their pros/cons.
\end{enumerate}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. We have also included a table to provide a comprehensive comparison of the related works. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanilla DQN and DDQN methods while providing a substantial improvement by 37.1\%\,--\,29.8\% in average QoE compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and the distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

\underline{Authors' Reply}: (a) Task sizes are chosen from a discrete set as most applications have tasks with predefined sizes. For instance, in image and video processing, tasks are typically divided into standardized sizes [X,XX,XXX]. Therefore, we assume that task sizes are selected randomly and uniformly from this discrete set. To address the reviewer’s comment and to provide further clarity regarding task sizes, we have revised the second paragraph of Section III as follows.

@@

\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_1} 
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\caption{\textcolor{blue}{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart1}
\end{figure}\vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart2}
\end{figure}\vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart3}
\end{figure} \vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_2} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_1}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

@@

Furthermore, to enhance the evaluation of our work, we have extended the performance analysis by comparing QECO with vanilla DQN and DDQN \cite{van2016deep}. This comparison illustrates the impacts of the LSTM network and dueling architecture. We have added Fig. 7 to Section V of the revised manuscript.

@@

\,\,\,\,We further investigate the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE. This metric signifies the advantages MDs obtain by utilizing different algorithms. \textcolor{blue}{Fig.~\ref{chart44} (a) shows the average QoE for different values of the task arrival rate. This figure highlights the superiority of the QECO algorithm in providing MDs with an enhanced experience. At lower task arrival rates (i.e., 50-150), QECO performs optimally and maintains an average QoE of at least 0.72, while the other methods experience a steeper decline, with average QoE dropping to 0--0.56. Specifically, at a task arrival rate of 200, QECO improves the average QoE by at least 65.7\% compared to other methods in the positive average QoE range. As task arrival rates increase to 300, the average QoE significantly decreases for all methods due to increased competition for resources in the MEC system. However, QECO still maintains a positive average QoE, while other methods fall to negative values, with a decline of up to -0.17. For higher task arrival rates (i.e., 350–450), QECO experiences a negative average QoE, but it shows at least a 42.6\%, 28.5\%, and 22.6\% smaller reduction in average QoE compared to RD, PGOA, and DCDRL, respectively.} \vspace{3mm}

\,\,\,\, Fig.~\ref{chart44} (b) illustrates the average QoE when we increase the number of MDs. The EN's workload grows when there are a larger number of MDs, leading to a reduction in the average QoE of all methods except LC. However, QECO effectively manages the uncertain load at the ENs. \textcolor{blue}{When the number of MDs increases from 30 to 110, QECO consistently maintains at least a 24.8\% higher QoE compared to the other methods. Specifically, at a moderate number of 70 MDs, QECO achieves an average QoE of 0.57, showing a 70.3\% and 44.7\% improvement compared to PGOA and DCDRL, respectively.} It is worth noting that although improvements in each of the QoE factors can contribute to enhancing system performance, it is essential to consider the user's demands in each time slot. Therefore, the key difference between QECO and other methods is that it prioritizes users' demands, enabling it to strike an appropriate balance among them, ultimately leading to a higher QoE for MDs.
 \vspace{3mm}\\\dots }}

@@

\,\,\,\, To capture the interactions between agents and the environment, we carefully simulated an MEC system that allows the DRL agents to gain experience and generate the data required in the proper format for training. As the agent interacts with the environment, it generates new data at each time step, using the system’s feedback (e.g., QoE) to adjust its actions. As mentioned in Section III of the revised manuscript, based on queuing theory, our simulated model provides key system performance metrics (e.g., task delay, energy consumption, etc.), which enable the agent to determine the mobile device's QoE and evaluate each state-action advantage value.\vspace{2mm}

\,\,\,\, For data generation, we adopt a scenario comprising 1,000 episodes. Each episode contains 100 time slots. During each time slot, mobile devices generate computation tasks based on a probabilistic task generation model. The DRL agents make offloading decisions for newly arrived tasks based on their state, which includes information such as task size, queue lengths, the mobile device’s energy level, and the workload history at the edge nodes. The agent evaluates the impact of its actions on the state by assessing the mobile device's QoE, which reflects key performance metrics based on user preferences. The system then transitions to the next state, enabling mobile devices to accumulate the necessary experience through interactions with the MEC environment. As detailed in Section IV-B, these experiences are stored in the replay buffer, creating a rich, continuously growing dataset that represents the diverse conditions and scenarios the agent encounters during computation offloading in MEC.\vspace{2mm}

@@

(c) Indeed, QECO improves the number of completed tasks by 14.4\% while at the same time reduces task delay and energy consumption by 9.2\% and 6.3\%, respectively. These together contribute to a significant improvement by 37.1\% in average QoE compared to \cite{yang2018distributed}. To clarify the improvement obtained by QECO, we have revised the abstract, Section I, and Section VI as follows.

@@

				Simulation results reveal that compared to the state-of-the-art existing work, QECO increases the number of completed tasks by 11.2\%\,--\,14.4\%, while simultaneously reducing task delay and energy consumption by 11.7\%\,--\,9.2\% and 9.8\%\,--\,6.3\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of at least 29.8\%\,--\,37.1\% compared to several existing algorithms.
}

@@

	\underline{Authors' Reply}: To address the reviewer's comment, we have carefully studied the recently published papers and revised the manuscript. 
	To be more specific, we have extended the literature review in Section II of the revised manuscript by providing a more comprehensive survey of the recently published state-of-the-art works and comparing their characteristics in Table \ref{table11}.
	We have also compared our work with more existing works and extended the performance evaluation in Section VI of the revised manuscript.

\vspace{3mm}
 The newly added Section II of the revised manuscript is as follows.

		\,\,\,\, Some studies explored task offloading problems in more advanced scenarios. Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
		To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent deep Q-network (DQN)-based algorithm.
		Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to concurrently optimize resource allocation and computation offloading.
		In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
		These works did not take into account the challenges of a dynamic network environment. For instance, in \cite{chen2021drl}, MDs are assumed to have sufficient transmission and computation resources from ENs, which may not always align with real-world conditions. While the works of \cite{wu2024privacy}--\cite{zhao2019deep} investigated the limited resources in MEC, they did not consider the dynamic workload at ENs in decision making processes, imposing significant challenges in overall system performance.

		\subsection{Queuing Theory for Efficient Resources Scheduling}
		\,\,\,\,To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.
		To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
		Liao \textit{et al.} in \cite{liao2023online} introduced a double DQN (DDQN)-based algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
		To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.
		In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. 
		Huang \textit{et al.} in \cite{huang2021deadline} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks.
		In above research \cite{munir2021multi}--\cite{huang2021deadline}, while queuing models were employed in several parts of the system, the offloading process was not approached as a holistic queuing system.

@@

		\begin{table*}[htbp]\textcolor{blue}{
				\renewcommand{\arraystretch}{0.6}
				\captionsetup{name=TABLE}
				\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
				\scalebox{0.7}{%
					\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
						\toprule
						\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
						\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
						\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
						\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
						%\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
						\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
						\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
						\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
						\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
						\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
						\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
						\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
						\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
						\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
						\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
						\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
						\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
						QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
						\toprule
				\end{tabular}}
				\label{table11}}
		\end{table*}\vspace{-5mm}

		\subsection{Task Offloading Considering EN's Workload}
		\,\,\,\,Due to the limited processing capacities of ENs, the processing capacity that an EN allocates to an MD depends on the EN's workload each time. Treating this dynamic workload as part of the environment can negatively impact system performance and requires careful consideration. Specifically, offloaded tasks may experience significant processing delays or be dropped if their deadlines expire. Some existing works have addressed the load levels at the edge nodes and proposed task offloading algorithms.
		Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the IIoT systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
		To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.
		Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
		Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
		In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.
		However, these algorithms in \cite{gong2022edge}–\cite{gao2022large} require global information of the system and may incur high signaling overhead.}

@@

@@

			\dots
	}}
\end{my}\vspace{6mm}

We have extended the evaluation of the QECO algorithm by comparing it with DCDRL \cite{qiu2020distributed}, which is a distributed algorithm for delay-sensitive tasks based on the actor-critic framework. This is the foundation for many state-of-the-art DRL algorithms, including DDPG and PPO. We have added this comparison to Section VI of the revised manuscript as follows: 
\begin{my}{1cm}{1cm}
	\rev{
		{\
			\color{black}
			\hspace{-10mm}  \dots \\ We use the following methods as benchmarks.
			\begin{itemize}
